Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-18 doc/mc-data.tex
Bug fixes in MICE
Added Lean checker data

Overall, we can summarize the results as:
\begin{itemize}
\item 84 total data points
\item 67 were completed by both programs in under 1000 seconds
\item Of those 21 were faster with MICE, 46 with CRAT
\item 7 completed with CRAT under 1000 seconds but exceeded that threshold for MICE
\item 1 completed with MICE under 1000 seconds but exceeded that threshold for CRAT
\item 9 completed with CRAT but generated errors for MICE.
\end{itemize}

>>>>

Overall, we can summarize the results as:
\begin{itemize}
\item 84 total data points
\item 76 were completed by both programs in under 1000 seconds
\item Of those 21 were faster with MICE, 55 with CRAT
\item 7 completed with CRAT under 1000 seconds but exceeded that threshold for MICE
\item 1 completed with MICE under 1000 seconds but exceeded that threshold for CRAT
\end{itemize}

\section{Benchmarking the \lean{} Proof Checker}

Ran \lean{} checker on the benchmarks yielding at most $10^7$ clauses, with time limit of 1000 seconds.
\begin{itemize}
\item 80 total
\item Had 2 that failed RUP check (need to investigate)
\item One of them needs to be rerun (Very long generation time)
\item Two timed out for \lean{}
\end{itemize}

\input{figure-check}

### 2023-03-18 doc/mc-paper.tex
Added Lean checker data

\subsection{Monolithic Forward Implication Proofs}

@@

\subsection{Impact of Optimizations}

@@

To assess the impact of the two optimizations: literal grouping and
lemmas, we ran the proof generator on the 80 problems for which the
combination of the two optimizations yielded proofs totaling at most
100~million clauses.  Compared to the problems used to assess monolithic
proof generation, this set included one that had a short proof but
long runtime and excluded four that had short runtimes but long
proofs.  We then ran the proof generator on all three combinations of
the optimizations being partially or totally disabled.
Figure~\ref{fig:optimized:lessoptimized} shows how disabling these optimizations affected the
total number of clauses in the proofs, where the X axis indicates the
total number with both optimizations enabled, while the Y axis
indicates the number with one (left) or both (right) optimizations
disabled.

>>>>

\subsection{Monolithic Forward Implication Proofs}
\label{app:experiment:monolithic}

@@

\subsection{Impact of Optimizations}
\label{app:experiment:optimize}

@@

To assess the impact of the two optimizations: literal grouping and
lemmas, we ran the proof generator on the 80 problems for which the
combination of the two optimizations yielded proofs totaling at most
10~million clauses.  Compared to the problems used to assess monolithic
proof generation (Section~\ref{app:experiment:monolithic}), this set included one that had a short proof but
long runtime and excluded four that had short runtimes but long
proofs.  We then ran the proof generator on all three combinations of
the optimizations being partially or totally disabled.
Figure~\ref{fig:optimized:lessoptimized} shows how disabling these optimizations affected the
total number of clauses in the proofs, where the X axis indicates the
total number with both optimizations enabled, while the Y axis
indicates the number with one (left) or both (right) optimizations
disabled.
